%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Research Intern} % Job title
{\href{http://www.nec-labs.com/}{\bf NEC Laboratories America, Inc.}}  % Organization
{Princeton, New Jersey, U.S.} % Location
{May. 2017 - Aug. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Analyzed historical activities of PCs in the company's internal networks and extract potential patterns can be considered as safe events.
		\item Built different prediction models for those patterns.
		\item Implemented the approach and integrated into Automated Security Intelligence (ASI) system of NEC.
	\end{cvitems}
}
	
	
%---------------------------------------------------------
\cventry
{Software Engineering Intern} % Job title
{\href{https://www.veritas.com/}{\bf Veritas Technologies LLC}}  % Organization
{Culver, California, U.S.} % Location
{May. 2016 - Aug. 2016} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Worked for the Platform team on EV.Cloud project.
		\item Applied topic modeling and machine learning techniques to intelligently suggest retention policies for customers' emails.
		\item Implemented and verified the proposed approach on Enron dataset using Spark, Hadoop, Cassandra, and Spring Framework.
		\item Was selected to present at VERITAS Cutting Edge 2016.
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {\href{http://www.sra.samsung.com}{\bf Samsung Research America}} % Organization
    {Irvine, Calirfornia, U.S.} % Location
    {Jun. 2015 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked for the Advanced Printing Software Lab.
        \item Completed the end-to-end scenario of extracting UP (Unified Interfaces of Samsung Printers) variability information from an actual MFP (Multi-Functions Printers), representing this in a UP variability model, editing this information, and using it to configure a running simulator instance.
        \item This involved design and implementation using different technologies: OSGi, EMF, Eclipse plug-ins, REST-ful webservices, UI development.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{http://www.handysoft.co.kr}{\bf Dasan Handysoft}} % Organization
    {Seoul, S.Korea} % Location
    {Sep. 2012 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item  Designed the server architecture of HandyUC 5.0, a platform providing various types of communication to enterprises, including email, instant messaging, and video conferencing.
        \item Implemented communication protocols of HandyUC, including XMPP protocol, Handysoft's legacy protocol, and a Http-based protocol.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PHP developer \& Asterisk PBX administrator} % Job title
    {HDC Media Vietnam} % Organization
    {Hanoi, Vietnam} % Location
    {Aug. 2009 - Jun. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item Developed a movie website based on Joomla platform to provide video contents to customers.
       \item Maintained and adapted Asterisk PBX system of the company to meet the company's requirements.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
