%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
\vspace{-1mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
\cventry
{Marcelo Schmitt Laser, \textbf{Duc M. Le}, Joshua Garcia, Nenad Medvidovic} % Role
{Architectural Archipelagos: Technical Debt in Long-Lived Software Research Platforms} % Event
{Mandrid, Spain} % Location
{May. 2021} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the International Conference on Technical Debt (TechDebt 2021)
	\end{cvitems}
}

\cventry
{\textbf{Duc M. Le}, Suhrid Karthik, Marcelo Schmitt Laser, Nenad Medvidovic} % Role
{Architectural Decay as Predictor of Issue-and Change-Proneness} % Event
{Stuttgart, Germany} % Location
{March. 2021} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the IEEE International Conference on Software Architecture (ICSA 2021)
	\end{cvitems}
}

\cventry
{Marcelo Schmitt Laser, \textbf{Duc M. Le}, Joshua Garcia, Nenad Medvidovic} % Role
{Arcade: an extensible workbench for architecture recovery, change, and decay evaluation} % Event
{Sacramento, U.S.} % Location
{Nov. 2020} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE 2021)
	\end{cvitems}
}

\cventry
{\textbf{Duc M. Le}, Daniel	Link, Arman	Shahbazian, Nenad Medvidovic} % Role
{An Empirical Study of Architectural Decay in Open-Source Software Systems} % Event
{Seattle, U.S.} % Location
{May. 2018} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the IEEE International Conference on Software Architecture (ICSA 2018)
	\end{cvitems}
}

\cventry
{Arman	Shahbazian, Youn Kyu Lee, \textbf{Duc M. Le}, Yuri Brun, Nenad Medvidovic} % Role
{Recovering architectural design decisions} % Event
{Seattle, U.S.} % Location
{May. 2018} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the IEEE International Conference on Software Architecture (ICSA 2018)
	\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Pooyan Behnamghader*, \textbf{Duc M. Le*}, Joshua Garcia, Daniel	Link, Arman	Shahbazian, Nenad Medvidovic} % Role
    {A Large-Scale Study of Architectural Evolution in Open-Source Software Systems} % Event
    {U.S. } % Location
    {Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item Empirical Software Engineering (EMSE) Journal 
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{\textbf{Duc M. Le}, Daniel	Link, Yixue Zhao, Arman	Shahbazian, Chris Mattmann, Nenad Medvidovic} % Role
{Toward a Classification Framework for Software Architectural Smells} % Event
{U.S. } % Location
{Feb. 2017} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Technical Report at USC Center for Systems and Software Engineering 
	\end{cvitems}
}
    

%---------------------------------------------------------
\cventry
{\textbf{Duc M. Le}, Nenad Medvidovic} % Role
{Architectural-Based Speculative Analysis to Predict Bugs in a Software System} % Event
{Austin, U.S.} % Location
{May. 2016} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the 38th International Conference on Software Engineering (ICSE), Doctoral Symposium track
	\end{cvitems}
}
	
%---------------------------------------------------------
\cventry
{\textbf{Duc M. Le}, Carlos Carrillo, Rafael Capilla, Nenad Medvidovic} % Role
{Relating Architectural Decay and Sustainability of Software Systems} % Event
{Venice, Italy} % Location
{Apr. 2016} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the 13th Working IEEE/IFIP Conference on Software Architecture (WICSA)
	\end{cvitems}
}


%---------------------------------------------------------
\cventry
{\textbf{Duc M. Le}, Pooyan Behnamghader, Joshua Garcia, Daniel	Link, Arman	Shahbazian, Nenad Medvidovic} % Role
{An Empirical Study of Architectural Change in Open-Source Software Systems} % Event
{Florence, Italy} % Location
{May. 2015} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the 12th Working Conference on Mining Software Repositories (MSR)
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{\textbf{Duc M. Le}, Lee Hyesun, Kyo C. Kang, Keun Lee } % Role
{Validating consistency between feature model and its implementation} % Event
{Pisa, Italy} % Location
{Jun. 2013} % Date(s)
{
	\begin{cvitems} % Description(s)
		\item Proceeding of the 13th International Conference on Software Reuse (ICSR)
	\end{cvitems}
}

%---------------------------------------------------------
\end{cventries}