%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------

\cventry
{Software Engineer} % Job title
{\href{http://www.bloomberg.com/}{\bf Bloomberg L.P.}}  % Organization
{New York, New York, U.S.} % Location
{Jul. 2018 - PRESENT} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Tech Lead of Authentication Platform; managed Bloomberg's enterprise-wide SSO system
	\end{cvitems}
}

\cventry
{Research Intern - Computer Security Group} % Job title
{\href{http://www.nec-labs.com/}{\bf NEC Laboratories America, Inc.}}  % Organization
{Princeton, New Jersey, U.S.} % Location
{May 2017 - Aug. 2017} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Built ML-based anomaly detection models for enterprise network security (integrated into NEC's ASI system)
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineering Intern - EV.Cloud Project, Platform Team} % Job title
{\href{https://www.veritas.com/}{\bf Veritas Technologies LLC}}  % Organization
{Culver, California, U.S.} % Location
{May 2016 - Aug. 2016} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Applied ML and topic modeling to intelligently suggest email retention policies using Spark and Hadoop
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Research Intern -  Advanced Printing Software Lab} % Job title
{\href{http://www.sra.samsung.com}{\bf Samsung Research America}} % Organization
{Irvine, California, U.S.} % Location
{Jun. 2015 - Sep. 2015} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item End-to-end product line engineering for Samsung multi-function printers using OSGi, EMF, and Eclipse
	\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{\href{http://www.handysoft.co.kr}{\bf Dasan Handysoft}} % Organization
{Seoul, S.Korea} % Location
{Sep. 2012 - Jun. 2013} % Date(s)
{
	\begin{cvitems} % Description(s) of tasks/responsibilities
		\item Designed server architecture for HandyUC 5.0 enterprise unified communications platform
	\end{cvitems}
}	
%---------------------------------------------------------
\end{cventries}
